---
title: "Technical"
author: "Madeline Gorchels"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
gas_data <- read_csv("Gas_Data_Tidy.csv") %>% 
  clean_names()

```

Work divide: Whoever finishes 1-2 does 5-6, other person does 3-4 and starts the memo 

***Part 1: Aggregate Daily Demand Curve

*****Math to get aggreate demand curve (set equal to qantity so we are adding horizontally)
low_q = 145837.7 + -5202.5*p
high_q = 147030.6 + -3293.0*p

Qag = 292868.3 + -8495.5*p


P_ag = 34.47334 + Q/-8495.5

P_ag = 34.47334 - 


```{r}
#equation math 
147030.6 + 145837.7

-5202.5 +-3293.0

292868.3/8495.5

```


```{r}
#quick plot
high_con = gas_data %>% 
  filter(class == "Q_High_Gallons_per_Day")

#linear model for the high income gas users 

high_lm <- lm(price_dollars ~ quantity, data = high_con)

high_lm <- lm(quantity ~ price_dollars, data = high_con)


high_lm <- lm(quantity ~ price_dollars, data = high_con)

summary(high_lm)

low_con = gas_data %>% 
  filter(class != "Q_High_Gallons_per_Day")

#linear model for the low income gas users


low_lm <- lm(price_dollars ~ quantity, data =low_con)

low_lm <- lm(quantity ~ price_dollars, data =low_con)


low_lm <- lm(quantity ~ price_dollars, data =low_con)

summary(low_lm)




demand_plot = ggplot(high_con, aes(x = quantity, y = price_dollars))+
  geom_smooth(method = "lm", se = FALSE)+
  theme_classic()+
  geom_smooth(data = low_con, aes(x = quantity, y = price_dollars), method = "lm", se = FALSE, color = "green")+
  geom_smooth(data = high_con, aes(x = quantity, y = price_dollars), method = "lm", se = FALSE, color = "purple")+
  geom_line(y = 2)

demand_plot
```

***Part 2: How is the current consumer benefit divided?

***Part 3: What are the effects of the 50 cent gas tax:
a. The amount of gasoline produced and sold in France.
b. The price of gasoline.
c. Welfare of “High” income consumers.
d. Welfare of “Low” income consumers.
e. Welfare of gas producers.
f. Total environmental damage.
g. Total revenue generated by the tax.