---
title: "Technical"
author: "Madeline Gorchels"
date: "4/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(janitor)
gas_data <- read_csv("Gas_Data_Tidy.csv") %>% 
  clean_names()

```

Work divide: Whoever finishes 1-2 does 5-6, other person does 3-4 and starts the memo 

***Part 1: Aggregate Daily Demand Curve

```{r}
#quick plot
high_con = gas_data %>% 
  filter(class == "Q_High_Gallons_per_Day")

low_con = gas_data %>% 
  filter(class != "Q_High_Gallons_per_Day")

demand_plot = ggplot(high_con, aes(x = quantity, y = price_dollars))+
  geom_smooth(method = "lm", se = FALSE)+
  theme_classic()+
  geom_smooth(data = low_con, aes(x = quantity, y = price_dollars), method = "lm", se = FALSE)+
  geom_line(y = 2)

demand_plot
```

***Part 2: How is the current consumer benefit divided?

***Part 3: What are the effects of the 50 cent gas tax:
a. The amount of gasoline produced and sold in France.
b. The price of gasoline.
c. Welfare of “High” income consumers.
d. Welfare of “Low” income consumers.
e. Welfare of gas producers.
f. Total environmental damage.
g. Total revenue generated by the tax.